---
title: "data-examples"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{data-examples}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(kumquat)

library(tidyverse)
library(colorspace)
```

There are four sample datasets in the package, with varying complexities in the decision boundary. 

The datasets are as follows.

- d_vertical
- d_oblique
- d_multi
- d_multitwo

All of these datasets are made for a binary classification task. Each dataset contains two numeric variables (`x`, `y`) and one categorical variable (`class`). In this section, we will visualize the datasets along with their decision boundary.

## `d_vertical` dataset

<!-- INFO: Combine these plots into one patchwork with titles for each one of them -->

```{r}
data("d_vertical")

ggplot(d_vertical, aes(x = x, y = y, colour = class)) +
  geom_point() +
  scale_colour_discrete_divergingx(palette = "Zissou 1") +
  theme_minimal() +
  theme(aspect.ratio = 1) +
  labs(title = "d_vertical dataset")
```

## `d_oblique` dataset

<!-- INFO: Combine these plots into one patchwork with titles for each one of them -->

```{r}
data(d_oblique, package="kumquat")
ggplot(data=d_oblique, aes(x = x, y = y, colour = class)) +
  geom_point() +
  scale_colour_discrete_divergingx(palette = "Zissou 1") +
  theme_minimal() +
  theme(aspect.ratio = 1) +
  labs(title = "d_oblique dataset")
```

## `d_multi` dataset

<!-- INFO: Combine these plots into one patchwork with titles for each one of them -->

```{r}
data("d_multi")

ggplot(d_multi, aes(x = x, y = y, colour = class)) +
  geom_point() +
  scale_colour_discrete_divergingx(palette = "Zissou 1") +
  theme_minimal() +
  theme(aspect.ratio = 1) +
  labs(title = "d_multi dataset")
```

## `d_multitwo` dataset

<!-- INFO: Combine these plots into one patchwork with titles for each one of them -->

```{r}
data("d_multitwo")

ggplot(d_multitwo, aes(x = x, y = y, colour = class)) +
  geom_point() +
  scale_colour_discrete_divergingx(palette = "Zissou 1") +
  theme_minimal() +
  theme(aspect.ratio = 1) +
  labs(title = "d_multitwo dataset")
```

## Testing kumquat with the given datasets

### Models

```{r}
library(randomForest)

rf_vertical <- randomForest(class ~ ., data = d_vertical)
rf_vertical_bundle <- bundle::bundle(rf_vertical)
```

```{r}
find_closest <- function(pt, data) {
  dst <- data |>
    mutate(dst = sqrt((x - pt$x)^2 + (y - pt$y)^2))
  return(which.min(dst$dst))
}
```


```{r}
pt <- tibble(x=0.3, y=0)
obs <- find_closest(pt, d_vertical)

ks <- kumquat(
  rf_vertical_bundle,
  d_vertical,
  obs,
  class_names = unique(d_vertical$class)
)
```

```{r}
# we expect the absolute importance of x to be greater for y
abs(ks[[1]]$local_model$importances["x"]) > abs(ks[[1]]$local_model$importances["y"])
```

